---
title: "Bergen & Grodner Replication Study Analysis (prereg)"
author: "Polina Tsvilodub"
date: "10/16/2020"
output: html_document
---

This script includes the preprocessing and analyses preregistered for our replication of the study by Bergen & Grodner "Speaker Knowledge Influences the Comprehension of Pragmatic Inferences" (2012).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include = FALSE}
library(tidyverse)
library(brms)
library(tidyboot)
```

```{r data, include=FALSE}
# read in data
data <- read_csv("~/Desktop/results-SPR-test.csv")

glimpse(data)
```
``` {r counts}
# some initial counts of the trial kinds for checking
data %>% count(type)
data %>% count(knowledge, trigger_type, continuation_type)
```

``` {r split_RTs}
# get main trials 
data_main <- data %>% 
  filter(trial_name == "self_paced_reading")

# wrangle: transform RT strings back into numbers 
data_int <- data_main %>% 
  # select relevant columns
  select(-X33, -QUD, -startDate, -startTime, -endTime, -timeSpent) %>%
  mutate(
  # make categorical predictors factors with correct levels for later contrast coding
  knowledge = factor(knowledge, levels = c("full", "partial")),
  trigger_type = factor(trigger_type, levels = c("scalar", "focused")),
  continuation_type = as.factor(continuation_type),
  # split RTs
  all_RTs_int = strsplit(all_reaction_times, "|", fixed = T),
  context_RTs_int = strsplit(context_reaction_times, "|", fixed = T),
  trigger_RTs_int = strsplit(trigger_reaction_times, "|", fixed = T),
  continuation_RTs_int = strsplit(continuation_reaction_times, "|", fixed = T)
)
glimpse(data_int)

# get filler trials (in case they're needed)
data_int_filler <- data_int %>% filter(type "filler")

# get critical main trials
data_int_critical <- data_int %>% filter(type == "main")

# split RTs into critical regions
data_int_split <- data_int_critical  %>%
  rowwise() %>%
  mutate(
  # for trigger sentences, only the first chunk is the critical one for scalar triggers (contains "some of")
  # the first two chunks are critical for focused triggers ("only" and "some of")
    # item 19 trigger sentence starts with another word 
  trigger_RT_only = ifelse(trigger_type =="focused", ifelse(ID == 19, trigger_RTs_int[2], trigger_RTs_int[1]), NA) %>% as.numeric(),
  trigger_RT_some = ifelse(trigger_type == "focused", ifelse(ID == 19, trigger_RTs_int[3], trigger_RTs_int[2]),
                           ifelse(ID == 19, trigger_RTs_int[2], trigger_RTs_int[1])) %>% as.numeric(),
  # in the continuation sentence, in the complement condition, the anaphora (first chunk) and 
  # the predicate (second chunk) are critical  
  continuation_RT_anaphora = ifelse(continuation_type != "scalar-cancelation", continuation_RTs_int[1], NA) %>%
    as.numeric(),
  continuation_RT_predicate = ifelse(continuation_type != "scalar-cancelation", continuation_RTs_int[2], NA) %>%
    as.numeric()
  # not yet sure what we need here 
  # continuation_RT_cancellation  
) 
glimpse(data_int_split)
# pivot to long format
data_int_split_long <- data_int_split %>% pivot_longer(cols = contains("_RT_"), names_to = "region", values_to = "critical_RTs") %>% drop_na("critical_RTs")
```

- some initial plots before exclusions
``` {r init_plots}
# plot dist of overall RTs per trial, by trial type 
data_main %>%
  ggplot(aes(x = time_spent, fill = type)) +
  geom_density(alpha = 0.3)

# plot overall RTs per trial by knowledge X trigger type in critical trials
data_int_critical %>%
  ggplot(aes(x = trigger_type, y = time_spent, fill = trigger_type)) +
  geom_boxplot(alpha = 0.3) +
  facet_grid(~knowledge)

# plot single RTs of critical regions by knowledge  
data_int_split_long %>%
  ggplot(aes(x = knowledge, y = critical_RTs, fill = knowledge)) +
  geom_boxplot(alpha = 0.3) +
  facet_grid(~region) 
```

- apply exclusion criteria: accuracy on questions > 0.8; exclude single RTs < 150 or > 2000
``` {r exclusions}
# submission_id column missing!
data_int_split_filter <- data_int_split_long %>% 
 # group_by(submission_id) %>% 
 # mutate(
 #   subj_acc = mean(correctness == T)
 #   ) %>%
 # ungroup() %>%
  # exclude participants with accuracy below 0.8
#  filter(subj_acc > 0.8,
  filter((critical_RTs > 150) & (critical_RTs < 2000))
```

- more plots after exclusions (mean RTs over critical regions and bootstrapped 95%-CIs)
 
```{r main_plots}
data_int_split_filter_summary <- data_int_split_filter %>%
  group_by(knowledge, trigger_type, region) %>% 
  tidyboot_mean(column = critical_RTs)

# plots TBD
```
- transformations : log-transform RTs
``` {r logs}
d_tidy_log_main <- data_int_split_filter %>%
  mutate(
    trigger_RT_only_log = log(trigger_RT_only),
    trigger_RT_some_log = log(trigger_RT_some),
    continuation_RT_anaphora_log = log(continuation_RT_anaphora),
    continuation_RT_predicate_log = log (continuation_RT_predicate)
  )
```

- stats: GLMMs
``` {r brm_models}
# contrast coding of the predictors
contrasts(d_tidy_log$knowledge) <- contr.sum(2)
contrasts(d_tidy_log$trigger_type) <- contr.sum(2)

# model 1: trigger RT ("some of")
model_trigger <- brm(
  trigger_RT_some_log ~ knowledge * trigger_type + (1 + knowledge * trigger_type | submission_id) + (1 | ID),
  data = d_tidy_log,
  iter = 3000,
  cores = 4
)

summary(model_trigger)

# model 2: continuation anaphora RT ("the others / the rest")
model_anaphora <- brm(
  continuation_RT_anaphora_log ~ knowledge * trigger_type + (1 + knowledge * trigger_type | submission_id) + (1 | ID),
  data = d_tidy_log,
  iter = 3000,
  cores = 4
)
summary(model_anaphora)
```
